---
title: "ADZUNA Job Salary Prediction"
output: html_document
---

Group project - Northwestern Uni

ADZUNA Job Salary Prediction
This project is a former Kaggle competition. Here is the problem description from the Kaggle website.
https://www.kaggle.com/c/job-salary-prediction

Problem Description
ADZUNA wants to build a prediction engine for the salary of any UK job ad, so they can make huge
improvements in the experience of users searching for jobs, and help employers and jobseekers
figure out the market worth of different positions. At the moment, approximately half of the UK job
ads they index have a salary publicly displayed. They need your help to bring more transparency to
this important market.

Adzuna has a large dataset (hundreds of thousands of records), which is mostly unstructured text,
with a few structured data fields. These can be in a number of different formats because of the
hundreds of different sources of records. Adzuna needs the help of the Kaggle community to figure
out the best techniques to apply to this data set to build a highly accurate predictive model for new
ads. You will build, train and test your salary prediction engines against a wide field of
competitors.

As an added perk, Adzuna intends to implement their chosen model on their website, both in the UK
and worldwide. You will have the satisfaction of seeing your work implemented in production and
change the way people search for jobs in the future.
Successful models will incorporate some analysis of the impact of including different keywords or
phrases, as well as making use of the structured data fields like location, hours or company. Some of
the structured data shown (such as category) is 'inferred' by Adzuna's own processes, based on where
an ad came from or its contents, and may not be "correct" but is representative of the real data.
You will be provided with a training data set on which to build your model, which will include all
variables including salary. A second data set will be used to provide feedback on the public
leaderboard. After approximately 6 weeks, Kaggle will release a final data set that does not include
the salary field to participants, who will then be required to submit their salary predictions against
each job for evaluation.


```{r}
adzuna = read.csv('~/Dropbox/NU/ADVANCED_MODELING/ADZUNA/datasets/Train_rev1.csv')
train = sample(1:nrow(adzuna),nrow(adzuna)*0.25) # 5% of total obs to begin manipulating the 
tr.adz = subset(adzuna, data=train)
head(tr.adz)
table(adzuna$Category) # see jobs by Category...
```

```{r}
head(adzuna)
trail(adzuna)

```

